Competing Bandits:\\ The Perils of Exploration under Competition \thanks{This is an extended abstract of \citet{CompetingBandits-merged}, which in turn subsumes conference papers \citet{CompetingBandits-itcs18} and \citet{CompetingBandits-ec19}.}

### 2020-09-24 journal paper/content/sec-model.tex
Added a sentence re agent models.

\asedit{\HardMaxRandom and \SoftMaxRandom can be realized as mixtures over more ``basic" agent types. Indeed,
\HardMaxRandom is a mixture of \HardMax and ``random" agents (which choose a principal uniformly at random). One can obtain a \SoftMaxRandom response function using agent types that choose a principal with a largest $\est_i$, unless $|\est_1-\est_2|$ is upper-bounded by some parameter $\theta$, in which case they choose uniformly. Then, we obtain \SoftMaxRandom as a mixture of random agents and these ``$\theta$-\HardMax'' agents, for a suitable distribution over $\theta$.}

>>>>

\asedit{\HardMaxRandom and \SoftMaxRandom can be seen as agent types that, resp., give some chance to the other principal and avoid sharp transitions in their probabilistic response. Alternatively, they can be realized as mixtures over more ``basic" agent types. Indeed, \HardMaxRandom is a mixture of \HardMax and ``random agents" (which choose a principal uniformly at random). One can obtain a \SoftMaxRandom response function using agent types that choose a principal $i$ with a largest reward estimate $\est_i$, unless $|\est_1-\est_2|$ is upper-bounded by some parameter $\theta$, in which case they choose uniformly. Then, we obtain \SoftMaxRandom as a mixture of random agents and these ``$\theta$-\HardMax'' agents, for a suitable distribution over $\theta$.}
